\begin{thebibliography}{10}

\bibitem{wordnet}Princeton University "About WordNet." WordNet. Princeton 
University. 2010. http://wordnet.princeton.edu \label{bib:wordnet}

\bibitem{WikiXML}WiktionaryX. 
http://redac.univ-tlse2.fr/lexiques/wiktionaryx.html. 
Franck Sajous. CLLE-ERSS. \label{bib:wikixml}

\bibitem{LittreXML}Littré, Émile. Dictionnaire de la langue française, 
Supplément. Paris, L. Hachette, 1878. Electronic version created by François 
Gannaz. http://www.littre.org \label{bib:littrexml}

\bibitem{MElt}Pascal Denis and Benoît Sagot (2012). Coupling an annotated 
corpus and a lexicon for state-of-the-art POS tagging. In Language Resources 
and Evaluation 46:4, pp. 721-736, DOI 10.1007/s10579-012-9193-0\label{bib:melt} 

\bibitem{lefff}Sagot (2010). The Lefff, a freely available and large-coverage 
morphological and syntactic lexicon for French. In Proceedings of the 7th 
international conference on Language Resources and Evaluation (LREC 2010), 
Istanbul, Turkey\label{bib:lefff} 

\bibitem{olnyetal}Olney J., Revard C. et Ziff P. (1968) Toward the development
 of computational aids for obtaining a formal semantic description of English.
System Development Corporation, Santa Monica\label{bib:olnyetal} 


\bibitem{word2vec}Mikolov T., Chen K., Corrado G. et Dean J. (2013)
Efficient Estimation of Word Representations in Vector Space. In
Proceedings of Workshop at ICLR.\label{bib:word2vec} 

\bibitem{gaumeetal}Gaume B., Hathout N. et Muller P. (2004)
Word Sense Disambiguation using a dictionary for sense similarity measure.
In Proceedings of the 20th international conference on Computational
Linguistics.\label{bib:gaumeetal} 

\bibitem{mulleretal}Muller P., Hathout N. et Gaume B. (2006)
Synonym extraction using a semantic distance on a dictionary.
In Proceding of the First Workshop on Graph Based Methods for
Natural Language Processing.\label{bib:mulleretal} 

\bibitem{traversmilgram}Travers J. et Milgram S. (1969)
An Experimental Study of the Small World Problem.
In Sociometry, Vol 32, No. 4, pp. 425-443\label{bib:traversmilgram} 

\bibitem{wattsstrogatz}Watts D. et Strogatz S. (1998)
Collective dynamics of 'small-world' networks
In Nature Vol 393 (6684), pp. 440-442 \label{bib:wattsstrogatz} 

\bibitem{veronis}Véronis J. (2004)
HyperLex: lexical cartography for information retrieval.
In Computer Speech and Language 18(3) pp 223-252. \label{bib:veronis} 

\bibitem{barabasi}Barabási A. et Albert R. (1999)
Emergence of scaling in random networks.
In Science 286 (5439) pp. 509-512 \label{bib:barabasi}

\bibitem{pagerank}Page L., Brin S., Motwani R. et Winograd T. (1998)
The pagerank citation ranking: Bringing order to the web.
Technical report, Stanford Digital Library Technologies Project.
\label{bib:pagerank}

\bibitem{linkanalysis}Leskovec A., Rajaraman A. et Ullman J. (2010)
Mining of Massive Datasets.
\label{bib:linkanalysis}

\bibitem{lesk}Lesk M. (1986)
Automatic sense disambiguation using machine readable dictionaries:
how to tell a pine cone from an ice cream cone.
In SIGDOC: Proceedings of the 5\textsuperscript{th} annual international
conference on Systems documentations pp 24-26 
\label{bib:lesk}

\end{thebibliography}
